---
title: "Example"
subtitle: "A complex and not so complex example"
author: Robert M. Porsch
bibliography: ref.bib
output: word_document
---



```{r, echo=F, message=F}
library(tidyverse)
data(iris)
```

# The *Iris* flower data set

The *Iris* flower data set is a multivariate data set introduced by Ronald Fisher in **1936**.
Also see @Fisher1936 for more information, but you also cite as this [@Fisher1936].

## This is a second header

One can compute the mean of variable $x$ (indexed by $i$) of size $P$ as 

$$\frac{1}{P} \sum^P_{i=1} x_i $$

Lists are also easy:

* one
* two
* three

You can also have numbered lists:

(@)  My first example will be numbered (1).
(@)  My second example will be numbered (2).

Explanation of examples.

(@)  My third example will be numbered (3).

**Numbering throughout the whole document**

1. First item
2. Second item
3. Third item

So it is all very ~~complicated~~ easy.

# Lets show some plots

```{r}
ggplot(iris, aes(x=Sepal.Length, y=Sepal.Width, color=Species)) + 
  geom_point()
```

* you can use the header of each code chunk to adjust figure size, caption and others
* Figures are relatively easy
* alternatively you can also save the file to disk and then import them

# Tables

```{r}
dd <- iris %>%
  gather("variable", "value", 1:4) %>%
  group_by(Species, variable) %>%
  summarise_each(funs(mean, sd, max, min))
knitr::kable(dd)
```

# Tables of Models

```{r}
library(pander)
n <- 100
x <- rnorm(n)
y <- 2*x + rnorm(n)
ll <- lm(y~x)
panderOptions("digits", 2)
pander(ll)
```

## Some notes in regards to tables

* Tables are tricky
* as more complicated as more difficult it gets
* consider writing in latex
* consider writing your papers in Markdown first and then do style adjustments later
* there are multiple templates for different journals

# Inline code

You can also have inline code.
So you can say that the mean of `Sepal.Width` is `r mean(iris$Sepal.Width)`.

# References



