---
title: "Research Pipelines"
subtitle: "Simplify Your Research"
author: Robert M. Porsch
output:
  ioslides_presentation:
    smaller: false
---

# The Idea

## A Pipeline


## Download and Formating

**Step 1:**
```{r, eval=F}
download.file("www.some_data.com/data.csv")
```

**Step 2:**
```{r, eval=F}
dat  <- read.csv("data.csv")
dat[,"Sum"] <- sum(dat[,1:2], na.rm=T)
write.csv(dat, "data_modified.csv")
```

**Step 3:**
```{r, eval=F}
dat <- read.csv("data_modified.csv")
analysis(dat)
```
* step 1 should be before step 2
* we should not repeat step 1 when we modify step 2
* use Makefiles


## What is a Makefile?

* `make` is an application which can execute make files
* Makefiles contain collection of commands
* keeps track of the last time files have been updated
* it contains a list of rules

```makefile
RULE: DEPENDENCY LINE
  ACTION LINE(S)
```

**DEPENDENCY LINE:**

<span style="color:red"> TARGET FILES </span>:
<span style="color:blue"> SOURCE FILES </span>

## Makefiles

```makefile
all: data.csv data_modidified.csv results.txt

clean:
  rm data.csv data_modidified.csv results.txt

data.csv:
  Rscript -e 'download.file("www.some_data.com/data.csv")'

data_modidified.csv: formating.R data.csv
  Rscript $<

results.txt: analysis.R data_modidified.csv
  Rscript $<
```

## Example

**Lets see how it looks like**


# Some Advanced Makefiles Stuff

## Define variables

```
data.csv: get_data.r
  R CMD BATCH get_data.r

RR := R CMD BATCH

data.csv: get_data.r
  $(RR) get_data.r
```

## Some other operators

```
histogram.png: histogram.tsv
	Rscript -e 'library(ggplot2); qplot(Length, Freq, data=read.delim("$<")); ggsave("$@")'
```

## Some more stuff

```
.PHONY: all clean
.DELETE_ON_ERROR:
.SECONDARY:
```

* `.PHONY` tells make that those are not files/directories
* `.DELETE_ON_ERROR` delete files of a target if it fails
* `.SECONDARY` prevents the deletion of intermediate files

## Some more stuff

```
all: $(Main)
  @echo Its done!!!
```

**Some other stuff**
```
plotting.txt: formating.r function.r
  Rscript $^ $@
```

* `$^` right side of `:`
* `$@` left side of `:`

## Exercise

**Use your the results and scripts from your previous task to write a makefile**
